### 2021-12-03 tex/linear.tex
[ writing ] WIP about DILL

\section{Intuitionistic linear logic}
\input{ill.tex}
\section{DILL}
DILL provides a syntax in which $\oc$ is characterised by a universal
property.
There is no need for any rule to depend on the entire context and rebind
variables (as done by BBdPH), so is more ND-like.
DILL makes $\oc$ behave more like a positive type former (see the deep
identity function $\oc A \vdash \oc A$).
DILL has been extended to dependent types: Vakar15.

The idea of split contexts can also be applied to left-/right-rule systems.
(Define this DILL variant.)

>>>>

\section{Intuitionistic linear logic}\label{sec:ill}
\input{ill.tex}

\section{DILL}
\input{dill.tex}
